Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-07-24 tables/estimatedparameters.tex
Remove threeparttable (for now)
no dleta rv hd47474

%!TEX root = ../nir_companions.tex
\begin{table*}
     \begin{threeparttable}[b]
        \small
        \centering
        \caption{Estimated flux ratios and semi-amplitude of the companion given the companion \(\textrm{M}_{2}/\textrm{M}_{2} \sin{i}\) from Table~\ref{tab:orbitparams}. The flux ratio \(F_{2}/F_{1} \) is calculated using the absolute \textit{K}-band magnitude difference of the host star to the Baraffe evolutionary model magnitude for the companion mass. The model ages used are those closest to host age value in Table~\ref{tab:starparams}, or the midpoint of the age range. The noise ratio is calculated via \(N_{2}/N_{1} = \sqrt{2} \times\sqrt{F_{1}/F_{2}}\). The orbital properties are calculated using the orbital parameters given above along with the times of observations in Table~\ref{tab:observations}.} 
        \begin{tabular}{l c c c c c c c c}
            \toprule
            &  Estimated  & Estimated &  Estimated & Estimated &  &    \\  % 2017
            Host           & \(\rm F_{2}/F_{1} \)   & \(\rm N_{2}/N_{1} \) (noise ratio) & \(\rm K_2\) &   \(\Delta RV\) & Phase coverage \\
            & \textit{K}-band     & & (kms\(^{-1}\)) & (ms\(^{-1}\)) & (\%) \\
            \midrule
            {HD 4747}        & \(3\times10^{-4} \)   & 76 &  -10.65 & -  &  -  \\  % 2017
            {HD 162020}   & \(7\times10^{-7} \)   & 1615  &  -98.92\tnote{a} &  2344.24     & 0.28~~  \\  %
            {HD 167665}    & \(2\times10^{-4} \)   &  105    &  -14.47\tnote{a}  &   138.45     & 0.18~~  \\  %  -- \(2\times10^{-5} \)  best case based on age rage.
            {HD 168443b} & \(1\times10^{-16} \)  &    \(1\times10^{8} \)   &  -64.65\tnote{a}&   257.16   & 0.035 \\ 
            {HD 168443c} &  \(1\times10^{-11} \)  &   \(4\times10^{5} \)     &  -18.05\tnote{a}  &   0.95   &  0.001 \\  %(c)
            {HD 202206}B  & \(8\times10^{-7} \)  &   1586 &  -6.79 & 145.17   & 0.74~  \\  %(B)   % May2017
            {HD 202206}c  &  \(5\times10^{-15}\)   &     \(2\times10^{7} \) &   -2.50     &   0.67     &  0.15~  \\  %(B)   % May2017
            {HD 211847}B  &  0.01 &  14   & $-$1.85 & 3.88   & 0.09~  \\  %B % 2017
            {HD 30501}      &  0.002  &  27  &  -16.12    &  1346.46      & 5.8~~  \\
            \bottomrule
            \end{tabular}
    \begin{tablenotes}
        \item[a] {Maximum \(K_2\) only given \(M_2 \sin{i}\)}
      \end{tablenotes}
    \end{threeparttable}
    \label{tab:flux_table}
\end{table*}

>>>>

%!TEX root = ../nir_companions.tex
\begin{table*}
  %   \begin{threeparttable}[b]
        \small
        \centering
        \caption{Estimated flux ratios and semi-amplitude of the companion given the companion \(\textrm{M}_{2}/\textrm{M}_{2} \sin{i}\) from Table~\ref{tab:orbitparams}. The flux ratio \(F_{2}/F_{1} \) is calculated using the absolute \textit{K}-band magnitude difference of the host star to the Baraffe evolutionary model magnitude for the companion mass. The model ages used are those closest to host age value in Table~\ref{tab:starparams}, or the midpoint of the age range. The noise ratio is calculated via \(N_{2}/N_{1} = \sqrt{2} \times\sqrt{F_{1}/F_{2}}\). The orbital properties are calculated using the orbital parameters given above along with the times of observations in Table~\ref{tab:observations}. {\rd There is no estimated \(\Delta RV\) for HD4747 since there was only one observation.}} 
        \begin{tabular}{l c c c c c c c c}
            \toprule
            &  Estimated  & Estimated &  Estimated & Estimated &  &    \\  % 2017
            Host           & \(\rm F_{2}/F_{1} \)   & \(\rm N_{2}/N_{1} \) (noise ratio) & \(\rm K_2\) &   \(\Delta RV\) & Phase coverage \\
            & \textit{K}-band     & & (kms\(^{-1}\)) & (ms\(^{-1}\)) & (\%) \\
            \midrule
            {HD 4747}        & \(3\times10^{-4} \)   & 76 &  -10.65 & -  &  -  \\  % 2017
            {HD 162020}   & \(7\times10^{-7} \)   & 1615  &  -98.92\tnote{a} &  2344.24     & 0.28~~  \\  %
            {HD 167665}    & \(2\times10^{-4} \)   &  105    &  -14.47\tnote{a}  &   138.45     & 0.18~~  \\  %  -- \(2\times10^{-5} \)  best case based on age rage.
            {HD 168443b} & \(1\times10^{-16} \)  &    \(1\times10^{8} \)   &  -64.65\tnote{a}&   257.16   & 0.035 \\ 
            {HD 168443c} &  \(1\times10^{-11} \)  &   \(4\times10^{5} \)     &  -18.05\tnote{a}  &   0.95   &  0.001 \\  %(c)
            {HD 202206}B  & \(8\times10^{-7} \)  &   1586 &  -6.79 & 145.17   & 0.74~  \\  %(B)   % May2017
            {HD 202206}c  &  \(5\times10^{-15}\)   &     \(2\times10^{7} \) &   -2.50     &   0.67     &  0.15~  \\  %(B)   % May2017
            {HD 211847}B  &  0.01 &  14   & $-$1.85 & 3.88   & 0.09~  \\  %B % 2017
            {HD 30501}      &  0.002  &  27  &  -16.12    &  1346.46      & 5.8~~  \\
            \bottomrule
            \end{tabular}
    \begin{tablenotes}
        \item[a] {Maximum \(K_2\) only given \(M_2 \sin{i}\)}
      \end{tablenotes}
%    \end{threeparttable}
    \label{tab:flux_table}
\end{table*}
